Approximation as Differentiation notes

### 2025-02-26 notes/sec/grothendieck.tex
Some progress on different g's.
Progress on using lambda of set-indexed products, not sure about the constant family though..
epsilon/lambda laws.
Tweaks.

\begin{proof}
Suppose $C$ locally small with binary biproducts given by $(\biprod,\inj,\proj)$ and set-indexed products
given by $(\prod,\pi)$. For any objects $X = (I, X), Y = (J, Y)$ and $Z = (K, Z)$ in $\Fam(C)$ define:

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[X, Y])$ in $\Fam(C)$ where we also write $[X,Y]$ for the
indexed family which maps every $(f: I \to J, g: X \to \reindex{Y}{f})$ in $\Fam(C)(X,Y)$ to $\prod_{i \in
I}\reindex{Y}{f}_i$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) which sends any morphism $(f: I \times J
\to K, g: X \times Y \to \reindex{Z}{f}): X \times Y \to Z$ to the morphism $(f': I \to \Fam(C)(Y,Z), g': X
\to \reindex{[Y, Z]}{f'}): X \to [Y, Z]$ with:
\begin{itemize}
\item $f'(i) = (f \comp (i, -): J \to K, \{g_{i,j} \comp \inj_{Y_j}\}_{j \in J}: Y \to \reindex{Z}{f \comp (i,
-)})$ where $\inj_{Y_j}: Y_j \to X_i \biprod Y_j$;
\item $g' = \{g_{i, j} \comp \inj_{X_i} \}_{i \in I}$ where $\inj_{X_i}: X_i \to X_i \biprod Y_j$;
\item $(-, i)$ is the reindexing function $j \mapsto (i, j): J \to I \times J$
\end{itemize}
\item $\eval_{X,Y}: [X, Y] \times X \to Y$
\end{enumerate}
\end{proof}

>>>>

\begin{proof}
Suppose $C$ locally small with binary biproducts given by $(\biprod,\inj,\proj)$ and set-indexed products
given by $(\prod,\eval_{\prod},\lambda_{\prod})$. For any objects $X = (I, X), Y = (J, Y)$ and $Z = (K, Z)$ in
$\Fam(C)$ define:

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[X, Y])$ in $\Fam(C)$ where we also write $[X,Y]$ for the
indexed family which maps every $(f: I \to J, g: X \to \reindex{Y}{f})$ in $\Fam(C)(X,Y)$ to $\prod_{i \in
I}\reindex{Y}{f}_i$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) which sends any morphism $(f: I \times J
\to K, g: X \times Y \to \reindex{Z}{f}): X \times Y \to Z$ to the morphism $(f': I \to \Fam(C)(Y,Z), g': X
\to \reindex{[Y, Z]}{f'}): X \to [Y, Z]$ with:
\begin{itemize}
\item $f'(i) = (f \comp (i, -): J \to K, \{g_{i,j} \comp \inj_{Y_j}\}_{j \in J}: Y \to \reindex{Z}{f \comp (i,
-)})$ where $\inj_{Y_j}: Y_j \to X_i \biprod Y_j$
\item $g' = \lambda_{\prod}(\{g_{i, j} \comp \inj_{X_i} \}_{i \in I})$ where $\inj_{X_i}: X_i \to X_i \biprod
Y_j$
\item $(-, i)$ is the reindexing function $j \mapsto (i, j): J \to I \times J$.
\end{itemize}
\item $\eval_{X,Y}: [X, Y] \times X \to Y$
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$:
\begin{enumerate}
\item $\eval_{Y,Z} \comp (\lambda_{X,Y,Z}(f) \times \id_{Y}) = f$
\item $\lambda^{-1}_{X,Y,Z}(\lambda_{X,Y,Z}(f)) = f$
\end{enumerate}
\todo{Prove this bit}
\end{proof}
